\Title

### 2016-02-14 manuscript/manuscript.tex
Caption for the SAm CV figure

\begin{figure}
    \centering
    \includegraphics{figures/south-america-residuals}
    \caption{
        Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a)
        shown as (a) a map and (b) a histogram with the calculated mean and
        standard deviation.
        (c) The value of the goal function (Eq.~\ref{eq:goalfunction})
        per Gauss-Newton iteration showing the convergence of the algorithm.
        Note that the y-axis is in logarithmic scale.
    }
    \label{fig:sam-residuals}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-cv}
    \caption{Cross-validation.}
    \label{fig:sam-cv}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/south-america-residuals}
    \caption{
        Residuals for the South American Moho inversion.
        The residuals are the observed data in Fig.~\ref{fig:sam-data}a
        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a.
        Shown as (a) a map and (b) a histogram with the calculated mean and
        standard deviation.
        (c) The value of the goal function (Eq.~\ref{eq:goalfunction})
        per Gauss-Newton iteration showing the convergence of the algorithm.
        Note that the y-axis is in logarithmic scale.
    }
    \label{fig:sam-residuals}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Cross-validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:sam-cv}
\end{figure}
